3D Environment Generation Using Conditional Adversarial Networks

### 2019-12-10 writing/paper/paper.tex
Write

	The resulting heightmaps can be imported into popular 3d modeling software including Unity, Unreal, Blender, and World Machine. For the purposes of visualizing these results, and because of the limited support for Linux in all of the previously listed softwares, we visualize results using a demo application called Fractscape. Fractscape includes elevation based texture mapping which happens to work very well for visualizing our terrain elevation data. Unity, Unreal, Blender and World Machine have a different workflow for painting textures, so using the generality of fractscape works best for our visualizations \cite{starscenesoftware2006}.

>>>>

	The resulting heightmaps can be imported into popular 3d modeling software including Unity, Unreal, Blender, and World Machine. For the purposes of visualizing these results, and because of the limited support for Linux, we visualize results using a demo application called Fractscape. Fractscape includes elevation based texture mapping which happens to work very well for visualizing our terrain elevation data. Unity, Unreal, Blender and World Machine all have different workflows for painting textures, so using the generality of fractscape works best for our visualizations \cite{starscenesoftware2006}.
